### 2016-04-14 response.md
revision

# Response to reviewers

We thank both reviewers for the insightful discussions.
Beyond their overall encouragement, they have identified terminological and conceptual errors on our parts and given additional methodological advice for which we are very grateful.
We note the reviewers were largely in agreement with regards to their overall evaluation and particular criticisms.
We have found it straight-forward to include all of their advice, and think this has greatly improved the manuscript.

In particular, reviewer #1 has pointed out that we employed the term parameter not only in the sense of e.g. a population parameter with which inference is concerned, but also incorrectly to refer to factors ("nuisance parameter").
In the reworked version of the manuscript, the term parameter is only employed in the sense of a population parameter to be estimated.
We have also corrected the other confusingly written or wrong uses of statistical terminology and concepts, such as those concerning variance in parameter estimation via multiple regression (which reviewer #2 has also pointed out).

Reviewer #2 (Jake Westfall) inquires about quantitative estimates of the failure rates of this approach.
We have amended the methods section with a short simulation, where we show that in the described procedure, in realistic contexts, failures (e.g. failures to reject confounded samples when a significant effect is only observed due to confounding) occur more often than correct rejections (e.g. correctly rejecting a sample for confound imbalance).

We have also rephrased multiple sections, shortened the discussion of collinearity, extended the discussions of the error of "accepting" the null, further emphasized the importance of providing descriptive statistics (which both reviewers have repeatedly asked for), reworked and shortened the confusingly written section on employing multiple regression to control for confounds (including a reference to Westfall & Yarkoni, 2016, which appeared just days after our initial submission).

### 2016-05-06 simulation/ui.R
fix stepping for sliders

@@ -29,16 +29,16 @@ shinyUI(fluidPage(
     sidebarPanel(h3("Simulation Parameters")
        ,sliderInput("manipulation.effect.size",
                    "Difference in outcome variable due to manipulation (Cohen's \\(d\\))",
-                   min = -10,
+                   min = -5,
                    max = 10,
                    value = 2,
-                   round = -1)
+                   step = 0.1)
        ,sliderInput("confound.feature.size",
                    "Difference in confounding feature between groups (Cohen's \\(d\\))",
-                   min = -10,
-                   max = 10,
-                   value = 1,
-                   round = -1)
+                   min = -5,
+                   max = 5,
+                   value = 1.0,
+                   step = 0.1)
        # ,sliderInput("confound.effect.size",
        #              "Difference in outcome variable due to confound (Cohen's \\(d\\))",
        #              min = -10,
@@ -50,13 +50,13 @@ shinyUI(fluidPage(
                     min = -1,
                     max = 1,
                     value = 1.0,
-                    round = -1)
+                    step = 0.1)
        ,sliderInput("n.items",
                     HTML("Number of items to draw </br > (from each manipulation-level)"),
                     min = 10,
                     max = 100,
                     value = 20,
-                    round = -1)
+                    step = 1)
        ,sliderInput("n.sims",
                     "Number of simulations to run",
                     min = 1,

### 2016-05-06 simulation/server.R
initial full simulation output

@@ -18,21 +18,31 @@
 library(shiny)
 # a near drop-in replacement for ggplot2 on the web
 library(plotly)
+library(car)
 library(plyr)
 library(reshape2)
 
 source("statfail.R")
 
-shinyServer(function(input, output) {
+shinyServer(function(input, output, session) {
 
   runSimulation <- reactive({
     # force update when user clicks on "Run Again"
     input$run
-    resimulate(n=input$n.sims
+    results <- resimulate(n=input$n.sims
               ,manipulation.effect.size=input$manipulation.effect.size
               ,confound.feature.size=input$confound.feature.size
               ,confound.feature.effect.correlation=input$confound.feature.effect.correlation
               ,n.items=input$n.items)
+
+    results$condition <- factor(results$condition,levels=c("control","manipulation"))
+    # since there are no other categorical variables to interact with, we keep
+    # it simple and use treatment coding. This allows a few shortcuts later, where
+    # we assume that the control=0 and treatment=1
+    options(decorate.contr.Treatment = "")
+    contrasts(results$condition) <- contr.Treatment(levels(results$condition))
+
+    results
   })
 
   runFeatureStats <- reactive({
@@ -45,37 +55,115 @@ shinyServer(function(input, output) {
     stats
   })
 
-  # runManipulationOurcomeStats <- reactive({
-  #   simulation <- runSimulation()
-  #   #simulation <- resimulate(n=3,manipulation.effect.size=2,confound.feature.size=1,confound.feature.effect.correlation=1,n.items=20)
-  #
-  #   x <- ddply(simulation,"iter",summarise,htest = t.test(confounded.outcome ~ condition,var.equal=TRUE))
-  #   x$field <- rep(c("t","df","p","conf.int","means","H0","tails","test","data"))
-  #   stats <- dcast(data=x, iter ~ field, value.var = "htest")
-  #   stats
-  # })
-  #
-  # runFeatureOutcomeStats <- reactive({
-  #   simulation <- runSimulation()
-  #   #simulation <- resimulate(n=3,manipulation.effect.size=2,confound.feature.size=1,confound.feature.effect.correlation=1,n.items=20)
-  #
-  #   x <- ddply(simulation,"iter",summarise,htest = t.test(confounded.outcome ~ condition,var.equal=TRUE))
[…]

### 2016-05-06 simulation/ui.R

@@ -65,6 +65,7 @@ shinyUI(fluidPage(
                                 # superlinear, perhaps roughly quadratic because of the way R does COW in its memory management
                     value = 1)
        ,actionButton("run",label = "Run simulation (again)")
+       ,width = 2
     ),
 
     # Show a plot of the generated distribution
@@ -73,16 +74,29 @@ shinyUI(fluidPage(
           tabPanel("Simulation"
                   ,h1("Single Simulation Results")
                   ,uiOutput("which.sim")
+                  ,h2("Detection with traditional tests")
                   ,fluidRow(column(4,plotlyOutput("plt.feature.distribution"))
                             ,column(4,plotlyOutput("plt.manipulation.regression"))
                             ,column(4,plotlyOutput("plt.feature.regression"))
                             )
-                  ,fluidRow(column(4,htmlOutput("feature.test")))
-                  ,plotlyOutput("plt.multiple.regression")
+                  ,fluidRow(column(4,htmlOutput("feature.test"))
+                            ,column(4,htmlOutput("manipulation.regression"))
+                            ,column(4,htmlOutput("feature.regression"))
+                            )
+                  ,h2("Multiple regression")
+                  ,fluidRow(column(8,plotlyOutput("plt.multiple.regression"))
+                            ,column(4,tableOutput("multiple.regression"),htmlOutput("multiple.regression.sigs")))
+                  ,h2("Comparison")
+                  ,htmlOutput("single.sim.results")
                   ,h1("Repeated Simulation Results")
+                  ,tableOutput("tbl.aggregate.results")
+                  # ,tabsetPanel(
+                  #   tabPanel("Feature distribution across groups", plotlyOutput("plt.feature.distribution.all"))
+                  #   ,tabPanel("Multiple regression", plotlyOutput("plt.multiple.regression.all"))
+                  # )
           )
-         ,tabPanel("Theoretical background",includeMarkdown("inference_failure.md"))
-         ,tabPanel("Debugging",tableOutput("testing.table"))
+          ,tabPanel("Simulation notes",includeMarkdown("simulation_notes.md"))
+          ,tabPanel("Theoretical background",includeMarkdown("inference_failure.md"))
        )
     )
   )

### 2016-05-08 simulation/server.R
refactoring more of the simulation out of the shiny app, code cleanup

@@ -46,123 +46,19 @@ shinyServer(function(input, output, session) {
   })
 
   runFeatureStats <- reactive({
-    simulation <- runSimulation()
-    #simulation <- resimulate(n=3,manipulation.effect.size=2,confound.feature.size=1,confound.feature.effect.correlation=1,n.items=20)
-
-    x <- ddply(simulation,"iter",summarise,htest = t.test(feature ~ condition,var.equal=TRUE))
-    x$field <- rep(c("t","df","p","conf.int","means","H0","tails","test","data"))
-    stats <- dcast(data=x, iter ~ field, value.var = "htest")
-    stats
+    compute.feature.stats( runSimulation() )
   })
 
   runManipulationRegression <- reactive({
-    simulation <- runSimulation()
-    #simulation <- resimulate(n=3,manipulation.effect.size=2,confound.feature.size=1,confound.feature.effect.correlation=1,n.items=20)
-
-    x <- ddply(simulation,"iter",summarise,
-               htest = {
-                 m <- lm(confounded.outcome ~ condition)
-                 c(as.list(summary(m)$coefficients),as.matrix(anova(m)))
-                 })
-    n_anova_params <- 2 # condition + residuals
-    n_lm_params <- 2    # Intercept + condition[manipulation]
-    n_anova_cols <- 5   # df, SS, MSS, F, p
-    n_lm_cols <- 4      # estimate, std. error, t, p
-
-    x$field <- rep( c(rep("estimate",n_lm_params)
-                      ,rep("std.err",n_lm_params)
-                      ,rep("t.val",n_lm_params)
-                      ,rep("p.val",n_lm_params)
-                      ,rep("df",n_anova_params)
-                      ,rep("SS",n_anova_params)
-                      ,rep("MSS",n_anova_params)
-                      ,rep("F.val",n_anova_params)
-                      ,rep("p.val",n_anova_params)
-                      ))
-    # first the terms of the LM, then the "terms" of the ANOVA
-    x$term <-  rep( c(
-                      rep(c("Intercept","condition[manipulation]"),n_lm_cols),
-                      rep(c("condition", "residual"), n_anova_cols)))
-    x$method <- rep( c(rep("lm",n_lm_params*n_lm_cols), rep("anova",n_anova_params*n_anova_cols)) )
-    stats <- dcast(data=x, iter  + term + method ~ field, value.var = "htest")
[…]

### 2016-05-08 simulation/statfail.R

@@ -15,10 +15,6 @@
 # You should have received a copy of the GNU Affero General Public License
 # along with this program.  If not, see <http://www.gnu.org/licenses/>.
 
-#n.items <- 20; manipulation.effect.size <- 2; confound.effect.size <- 0.5; confound.feature.size <- 0.5; confound.feature.effect.correlation <- 1;
-#library(MASS)
-#confound.feature.effect.correlation
-#confound.feature.size
 library(reshape2)
 library(plyr)
 
@@ -99,12 +95,6 @@ simulate <- function(manipulation.effect.size, confound.feature.size,
   results
 }
 
-# x <- simulate(manipulation.effect.size=2,confound.feature.size=1,confound.feature.effect.correlation=0.8,n.items=20)
-# summary(lm(outcome ~ condition, data=x))
-# t.test(outcome~condition,data=x)
-# t.test(confounded.outcome~condition,data=x)
-# t.test(feature~condition,data=x)
-
 resimulate <- function(n,...){
   # strip out the iteration number being passed via lapply
   lambda <- function(x,...) simulate(...)
@@ -117,4 +107,155 @@ resimulate <- function(n,...){
   result
 }
 
-#resimulate(n=100,manipulation.effect.size=2,confound.feature.size=1,confound.feature.effect.correlation=0.8,n.items=20)
+compute.feature.stats <- function(simulation){
+  # allow for processing of a single simulated dataset generated with simulate()
+  if( !("iter" %in% names(simulation)) ) {
+    simulation$iter <- 1
+  }
+
+  x <- ddply(simulation,"iter",summarise,htest = t.test(feature ~ condition,var.equal=TRUE))
+  x$field <- rep(c("t","df","p","conf.int","means","H0","tails","test","data"))
+  stats <- dcast(data=x, iter ~ field, value.var = "htest")
+  stats
+}
+
+compute.manipulation.regression <- function(simulation){
+  # allow for processing of a single simulated dataset generated with simulate()
+  if( !("iter" %in% names(simulation)) ) {
+    simulation$iter <- 1
+  }
+
+  x <- ddply(simulation,"iter",summarise,
+             htest = {
+               m <- lm(confounded.outcome ~ condition)
+               c(as.list(summary(m)$coefficients),as.matrix(anova(m)))
+             })
+  n_anova_params <- 2 # condition + residuals
[…]

### 2016-05-08 simulation/ui.R

@@ -39,12 +39,6 @@ shinyUI(fluidPage(
                    max = 5,
                    value = 1.0,
                    step = 0.1)
-       # ,sliderInput("confound.effect.size",
-       #              "Difference in outcome variable due to confound (Cohen's \\(d\\))",
-       #              min = -10,
-       #              max = 10,
-       #              value = 1,
-       #              round = -1)
        ,sliderInput("confound.feature.effect.correlation",
                     "Impact of confounding feature (correlation between measured confounding feature and outcome variable)",
                     min = -1,

### 2016-05-08 simulation/statfail.R
support for parallel simulation

@@ -95,11 +95,11 @@ simulate <- function(manipulation.effect.size, confound.feature.size,
   results
 }
 
-resimulate <- function(n,...){
+resimulate <- function(n,...,lapply.fnc=lapply){
   # strip out the iteration number being passed via lapply
   lambda <- function(x,...) simulate(...)
 
-  x <- lapply(1:n,lambda,...)
+  x <- lapply.fnc(1:n,lambda,...)
   result <- do.call(rbind,x)
 
   result$iter <- sort(rep(seq(n),nrow(result)/n))
@@ -107,19 +107,19 @@ resimulate <- function(n,...){
   result
 }
 
-compute.feature.stats <- function(simulation){
+compute.feature.stats <- function(simulation,...){
   # allow for processing of a single simulated dataset generated with simulate()
   if( !("iter" %in% names(simulation)) ) {
     simulation$iter <- 1
   }
 
-  x <- ddply(simulation,"iter",summarise,htest = t.test(feature ~ condition,var.equal=TRUE))
+  x <- ddply(simulation,"iter",summarise,htest = t.test(feature ~ condition,var.equal=TRUE),...)
   x$field <- rep(c("t","df","p","conf.int","means","H0","tails","test","data"))
   stats <- dcast(data=x, iter ~ field, value.var = "htest")
   stats
 }
 
-compute.manipulation.regression <- function(simulation){
+compute.manipulation.regression <- function(simulation,...){
   # allow for processing of a single simulated dataset generated with simulate()
   if( !("iter" %in% names(simulation)) ) {
     simulation$iter <- 1
@@ -129,7 +129,7 @@ compute.manipulation.regression <- function(simulation){
              htest = {
                m <- lm(confounded.outcome ~ condition)
                c(as.list(summary(m)$coefficients),as.matrix(anova(m)))
-             })
+             },...)
   n_anova_params <- 2 # condition + residuals
   n_lm_params <- 2    # Intercept + condition[manipulation]
   n_anova_cols <- 5   # df, SS, MSS, F, p
@@ -158,7 +158,7 @@ compute.manipulation.regression <- function(simulation){
   stats
 }
 
-compute.feature.regression <- function(simulation){
+compute.feature.regression <- function(simulation,...){
   # allow for processing of a single simulated dataset generated with simulate()
   if( !("iter" %in% names(simulation)) ) {
     simulation$iter <- 1
@@ -168,7 +168,7 @@ compute.feature.regression <- function(simulation){
[…]

### 2016-05-08 simulation/ui.R
minor GUI tweaking

@@ -78,8 +78,8 @@ shinyUI(fluidPage(
                             ,column(4,htmlOutput("feature.regression"))
                             )
                   ,h2("Multiple regression")
-                  ,fluidRow(column(8,plotlyOutput("plt.multiple.regression"))
-                            ,column(4,tableOutput("multiple.regression"),htmlOutput("multiple.regression.sigs")))
+                  ,fluidRow(column(7,plotlyOutput("plt.multiple.regression"))
+                            ,column(5,h3("Linear Model"),tableOutput("multiple.regression"),h3("ANOVA"),htmlOutput("multiple.regression.sigs")))
                   ,h2("Comparison")
                   ,htmlOutput("single.sim.results")
                   ,h1("Repeated Simulation Results")

### 2016-05-08 simulation/ui.R
note on interpretating multiple regression output

@@ -78,7 +78,7 @@ shinyUI(fluidPage(
                             ,column(4,htmlOutput("feature.regression"))
                             )
                   ,h2("Multiple regression")
-                  ,fluidRow(column(7,plotlyOutput("plt.multiple.regression"))
+                  ,fluidRow(column(7,plotlyOutput("plt.multiple.regression"),includeMarkdown("interpret_multiple.md"))
                             ,column(5,h3("Linear Model"),tableOutput("multiple.regression"),h3("ANOVA"),htmlOutput("multiple.regression.sigs")))
                   ,h2("Comparison")
                   ,htmlOutput("single.sim.results")

### 2016-05-08 simulation/ui.R
added an about tab to the simulation

@@ -91,6 +91,7 @@ shinyUI(fluidPage(
           )
           ,tabPanel("Simulation notes",includeMarkdown("simulation_notes.md"))
           ,tabPanel("Theoretical background",includeMarkdown("inference_failure.md"))
+          ,tabPanel("About",includeMarkdown("about.md"))
        )
     )
   )

### 2016-05-08 simulation/statfail.Rmd
static simulation across various parameter settings

---
title: 'Inference failure: Confound and control in BBS experiments'
author: "Phillip M. Alday"
date: "May  2016"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    self_contained: TRUE
    highlight: textmate
params:
  n: 500
  use_plotly: FALSE
---

# Read the paper
Sassenhagen, Jona and Phillip M. Alday (under review): A common misapplication of statistical inference: nuisance control with null-hypothesis significance tests. Brain & Language. [arXiv preprint](http://arxiv.org/abs/1602.04565). [Repository](https://github.com/jona-sassenhagen/statfail/).

The title will probably change in the near feature, as some of our initial reviewer feedback has been some very helpful terminological suggestions.

Another Python-based simulation will soon be made available on Binder, but the preliminary code is already in the GitHub repository.

A Shiny app that allows you to more closely individual simulated experiments for a given set of simulation parameters is available in the GitHub repository. This will be posted on [shinyapps.io](https://www.shinyapps.io/) as soon as we RStudio updates their server version of R or we have a chance to install and test an extra, older version of R.

# Simulation
Here, we repeat the simulation in the Shiny app, but iterate over different possibilities for

1. **manipulation effect size:** the effect size from the manipulation of interest
2. **confound feature size:** the measured size of the confounding feature
3. **confound feature-effect correlation:**the correlation between that measured size the and the effect size of the feature

The last two emphasize a subtle point -- one of the many problems with doing inferential tests on group attributes (e.g. word frequency vs. condition in language studies) is that you're testing the difference in the feature and not the impact of that (difference in the) feature on the outcome. 
In other words, you're assuming that the measured feature difference exactly correlates with the impact that feature has on the outcome, which is a fairly strong assumption.

## Setup

```{r setup, include=FALSE}
set.seed(42) # use a fixed random seed for reproducability

# use some parallel magic to speed things long
library(parallel)
options(mc.cores=2)
library(doMC)
library(foreach)
registerDoMC(2)

library(reshape2)
library(plyr)
library(ggplot2)
# if plotly isn't loaded, then just pass through ggplot's output
if(params$use_plotly){ 
  library(plotly) 
}else{
  ggplotly <- function(x) x
}
# this is the meat of the simulation
source("statfail.R")
```

The difficult part of the simulation is performed by `statfail.R`, which is shared with the Shiny app.
Both the source code and an explanation of the general principles (`simulation_notes.md`) are available in the GitHub repository.
Here, we only need to iterate over a few possibilities for the manipulation effect size, confound feature size and confound feature-effect correlation.
The number of simulated experiments is held constant for all combinations of these (set via the document parameter `n`, which had the value `r params$n` when this document was generated).
Increasing this value will of course help detect rare phenomena, but will drastically increase time and memory needed.

```{r simulate, cache = TRUE,message=FALSE,dependson=params}
results <- data.frame()
for(mes in seq(0,2,by=0.5)){
  for(cfs in seq(0,2,by=0.5)){
    for(cfec in c(0, 0.1, 0.3, 0.5, 0.8, 1)){  
      input <- list(n.sims=params$n,
                manipulation.effect.size=mes,               # in Cohen's d
                confound.feature.size=cfs,                  # in Cohen's d
                confound.feature.effect.correlation = cfec, # Pearson
                n.items=20)
      simulation <- resimulate(n=input$n.sims
                      ,manipulation.effect.size=input$manipulation.effect.size
                      ,confound.feature.size=input$confound.feature.size
                      ,confound.feature.effect.correlation=input$confound.feature.effect.correlation
                      ,n.items=input$n.item
                      ,lapply.fnc=mclapply)

      pretest <- compute.feature.stats(simulation,.parallel=TRUE)
      manipulation <- compute.manipulation.regression(simulation,.parallel=TRUE)
      feature <- compute.feature.regression(simulation,.parallel=TRUE)
      multiple <- compute.multiple.regression(simulation,.parallel=TRUE)

      r <- compute.aggregate.results(pretest,manipulation,feature,multiple)
      cmp <- mclapply(r,function(x) x < 0.05)
      cmp <- as.data.frame(cmp)

      ## the rejections based on the pretest
      rejections <- sum(cmp$pretest) / input$n.sims
      manipulation_still_significant <- sum(with(subset(cmp,pretest), manipulation.multiple)) / input$n.sims
      feature_has_no_effect <- sum(with(subset(cmp,pretest), !feature.simple)) / input$n.sims
      feature_irrelevant_in_multiple <- sum(with(subset(cmp,pretest), !feature.multiple)) / input$n.sims

      ## the acceptances based on the pretest
      not_rejected <- (input$n.sims - rejections) / input$n.sims
      feature_relevant_in_multiple <- sum(with(subset(cmp,!pretest), feature.multiple)) / input$n.sims
      manipulation_only_in_simple <-  sum(with(subset(cmp,!pretest), manipulation.simple & !manipulation.multiple)) / input$n.sims

      rsum <- data.frame(rejections
                         ,manipulation_still_significant
                         ,feature_has_no_effect
                         ,feature_irrelevant_in_multiple
                         ,not_rejected
                         ,feature_relevant_in_multiple
                         ,manipulation_only_in_simple
                         ,mes,cfs,cfec)

      results <- rbind(results, rsum)
    }
  }
}

# Convert the data to long format for easy plotting
rejections <- melt(results
                   ,id.vars=c("mes","cfs","cfec")
                   ,measure.vars=c("rejections"
                                   ,"manipulation_still_significant" 
                                   ,"feature_has_no_effect"
                                   ,"feature_irrelevant_in_multiple")
                   ,variable.name="type"
                   ,value.name = "percent.studies")
rejections$result <- "reject"

acceptances <- melt(results
                    ,id.vars=c("mes","cfs","cfec")
                    ,measure.vars=c("not_rejected"
                                    ,"feature_relevant_in_multiple"
                                    ,"manipulation_only_in_simple")
                    ,variable.name="type"
                    ,value.name = "percent.studies")
acceptances$result <- "accept"

results.long <- join(rejections,acceptances,type="full")
results.long$percent.studies <- results.long$percent.studies * 100
```

## Generate graphics
```{r generate.graphics, dependson='simulate',cache=TRUE,message=FALSE}
# prettier names for the legend
results.long$type <-factor(results.long$type
                           ,levels=c("rejections"
                                     ,"manipulation_still_significant"
                                     ,"feature_has_no_effect"
                                     ,"feature_irrelevant_in_multiple"
                                     ,"not_rejected"
                                     ,"feature_relevant_in_multiple"
                                     ,"manipulation_only_in_simple")
                           ,labels = c("rejected"
                                       ,"but significant manipulation missed"
                                       ,"when feature was not significant in simple regression"
                                       ,"when feature was not significant in multiple regression"
                                       ,"accepted"
                                       ,"but feature still had an effect in multiple regression",
                                       "and the manipulation was only significant in simple regression"))

# This uses the deprecated labeller API for ggplot.
facet_labeller <- function(variable,value){
  lbl <- NULL
  if (variable=='cfs') {
    lbl <- paste("Feature:",value)
  }else if (variable == 'mes') {
    lbl <- paste("Manipulation:",value)
  }else if (variable == 'cfec') {
    lbl <- paste("Feature-size/effect correlation:",value)
  } else {
    lbl <- as.character(value)
  }
}

# generate the graphic for rejections
gg.reject <- ggplot(subset(results.long,result=="reject"),aes(color=type,x=cfec,y=percent.studies)) +
  geom_line(stat="identity") + 
  facet_grid(cfs ~ mes,labeller = facet_labeller) + 
  xlab("Correlation of feature as measured and effect of feature on outcome") + 
  ylab("Percent of simulated studies") + 
  theme(legend.position="top") + #coord_fixed(ratio=1/100) +
  guides(color=guide_legend(title="Result based on inferential pretesting of measured feature",
                            title.position="top",
                            nrow=2))

# generate the same graphic for acceptances
gg.accept <- gg.reject %+% subset(results.long,result=="accept")

```

# Results  {.tabset .tabset-fade .tabset-pills}
The results in the following are whether or not a particular experimental manipulation was "allowed", i.e. accepted or rejected, based on inferential testing on the difference in confounding feature between experimental groups.

- *Manipulation* is the effect size in Cohen's $d$ from the experimental manipulation.
- *Feature* is the difference in Cohen's $d$ of the confounding feature between groups (again **not** its effect).

## Rejections
* Rejections where the significant manipulation was missed are an example of throwing the baby out with the bathwater.
* Rejections where the confounding feature was not a significant predictor in simple or multiple regression are arguably rejections where there is no effect of the feature.

```{r reject, echo=FALSE, fig.align="center", cache=FALSE}
ggplotly(gg.reject)
```

## Acceptances
* Acceptances where the feature still had an effect in multiple rejection are failed detections of a real confounding effect.
* Acceptances where the manipulation was only significant in simple regression are failed detections of a real confounding effect *that completes subsumes the manipulation effect*.

```{r accept, echo=FALSE, fig.align="center", cache=FALSE}
ggplotly(gg.accept)
```

### 2016-05-09 simulation/statfail.Rmd
parameter for number of cores in multiprocessing

@@
   use_plotly: FALSE
+  cores: 2
 ---
@@
 library(parallel)
-options(mc.cores=2)
+options(mc.cores=params$cores)
 library(doMC)
 library(foreach)
-registerDoMC(2)
+registerDoMC(params$cores)
 

### 2016-05-09 simulation/ui.R
fix dependency issue, update ignore

@@ -17,6 +17,8 @@
 
 library(shiny)
 library(plotly)
+# add this so that the includeMarkdown() stuff works on shinyapps.io
+library(rmarkdown)
 
 shinyUI(fluidPage(
 

### 2016-05-09 simulation/statfail.Rmd
crossref, request to run locally

@@
 
-A Shiny app that allows you to more closely individual simulated experiments for a given set of simulation parameters is available in the GitHub repository.
-This will be posted on [shinyapps.io](https://www.shinyapps.io/) as soon as we RStudio updates their server version of R or we have a chance to install and test an extra, older version of R.
+A Shiny app that allows you to more closely individual simulated experiments for a given set of simulation parameters is available in the GitHub repository and on [shinyapps.io](https://palday.shinyapps.io/statfail/).
+If you're going to do lots of computations, please run the app locally so that server time remains available for others.
 

### 2016-05-09 simulation/ui.R

@@ -25,6 +25,7 @@ shinyUI(fluidPage(
   # Application title
   titlePanel("Inference failure: Confound and control in BBS experiments"),
   withMathJax(),
+  HTML("<i>If you're going to do lots of computations, please run the app locally so that server time remains available for others.</i>"),
 
   # Sidebar with a slider input for number of bins
   sidebarLayout(

### 2016-05-09 simulation/statfail.Rmd
bug fix in aggregation/graphics

@@
       ## the acceptances based on the pretest
-      not_rejected <- (input$n.sims - rejections) / input$n.sims
+      not_rejected <-  sum(!cmp$pretest) / input$n.sims
       feature_relevant_in_multiple <- sum(with(subset(cmp,!pretest), feature.multiple)) / input$n.sims

### 2016-05-09 simulation/server.R
render beta as number

@@ -221,7 +221,7 @@ shinyServer(function(input, output, session) {
 
     stats.lm
 
-  },include.rownames=TRUE,digits=c(0,2,2,2,2),display=c("s","s","g","f","g"))
+  },include.rownames=TRUE,digits=c(0,2,2,2,2),display=c("s","g","g","f","g"))
 
   output$multiple.regression.sigs <- renderTable({
     stats <- runMultipleRegression()

### 2016-05-20 simulation/ui.R
copy-paste error in the license

@@ -2,7 +2,7 @@
 #
 # This file is part of statfail.
 #
-# Optional Stopping is free software: you can redistribute it and/or modify
+# Statfail is free software: you can redistribute it and/or modify
 # it under the terms of the GNU Affero General Public License as published by
 # the Free Software Foundation, either version 3 of the License, or
 # (at your option) any later version.

### 2016-05-20 response.md
starting on integrating simulations
simulation added to manuscript

@@
 In particular, reviewer #1 has pointed out that we employed the term parameter not only in the sense of e.g.
-a population parameter with which inference is concerned, but also incorrectly to refer to factors ("nuisance parameter").
+a population parameter with which inference is concerned, but also incorrectly to refer to (confounding) covariates ("nuisance parameter").
 In the reworked version of the manuscript, the term parameter is only employed in the sense of a population parameter to be estimated.
@@
 We have also rephrased multiple sections, shortened the discussion of collinearity, extended the discussions of the error of "accepting" the null, further emphasized the importance of providing descriptive statistics (which both reviewers have repeatedly asked for), reworked and shortened the confusingly written section on employing multiple regression to control for confounds (including a reference to Westfall & Yarkoni, 2016, which appeared just days after our initial submission).
+Finally, we have included a simulation that demonstrates the impact of the problem.

### 2016-05-20 generate_sim_graphics_for_paper.R

@@ -1,0 +1,39 @@
+# Copyright 2016, Phillip Alday
+#
+# This file is part of statfail.
+#
+# Statfail is free software: you can redistribute it and/or modify
+# it under the terms of the GNU Affero General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU Affero General Public License for more details.
+#
+# You should have received a copy of the GNU Affero General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
+# This script just extracts the static simulation (published on RPubs) and
+# runs it to create graphics for the paper.
+# This guarantees that the figures and simulation are the same for both.
+
+library(knitr)
+script <- tempfile()
+# extract code
+params <- data.frame(n=5000,cores=parallel::detectCores(),use_plotly=FALSE)
+purl('simulation/statfail.Rmd',output=script, documentation=0)
+code <- scan(script,what="character",sep="\n")
+# remove the plot displaying bits
+code <- code[grep("ggplotly",code,invert=TRUE)]
+# skip the bit where RMarkdown sets the params field
+code <- code[4:length(code)]
+# execute the simulation
+startwd <- setwd(normalizePath('simulation'))
+eval(parse(text=code))
+
+setwd(startwd)
+# save the graphics
+ggsave("sim-accept.pdf",gg.accept,width=7.5,height=6)
+ggsave("sim-reject.pdf",gg.reject,width=7.5,height=6)

### 2016-05-20 response.md
resubmission

@@
 In the reworked version of the manuscript, the term parameter is only employed in the sense of a population parameter to be estimated.
+We instead employ the term "nuisance variable" to refer to that which we had previously incorrectly called "nuisance parameter".
 We have also corrected the other confusingly written or wrong uses of statistical terminology and concepts, such as those concerning variance in parameter estimation via multiple regression (which reviewer #2 has also pointed out).
@@
 
-We have also rephrased multiple sections, shortened the discussion of collinearity, extended the discussions of the error of "accepting" the null, further emphasized the importance of providing descriptive statistics (which both reviewers have repeatedly asked for), reworked and shortened the confusingly written section on employing multiple regression to control for confounds (including a reference to Westfall & Yarkoni, 2016, which appeared just days after our initial submission).
+We have also rephrased multiple sections for style, shortened the discussion of collinearity, extended the discussions of the error of "accepting" the null, further emphasized the importance of providing descriptive statistics (which both reviewers have repeatedly asked for), reworked and shortened the confusingly written section on employing multiple regression to control for confounds (including a reference to Westfall & Yarkoni, 2016, which appeared just days after our initial submission).
 Finally, we have included a simulation that demonstrates the impact of the problem.
+
+We again wish to thank the reviewers for their fair and constructive criticism.

### 2016-07-06 simulation/ui.R
match title to paper

@@ -23,7 +23,7 @@ library(rmarkdown)
 shinyUI(fluidPage(
 
   # Application title
-  titlePanel("Inference failure: Confound and control in BBS experiments"),
+  titlePanel("A common misapplication of statistical inference: nuisance control with null-hypothesis significance tests"),
   withMathJax(),
   HTML("<i>If you're going to do lots of computations, please run the app locally so that server time remains available for others.</i>"),
 

### 2016-07-06 simulation/statfail.Rmd
missing space
slight improvements in graphics, hopefully clearer phrasing (that also matches new phrasing in paper)

@@
 ---
-title: 'Inference failure: Confound and control in BBS experiments'
+title: 'A common misapplication of statistical inference: nuisance control with null-hypothesis significance test'
 author: "Phillip M. Alday"
@@
 
-Another Python-based simulation will soon be made available on Binder, but the preliminary code is already in the GitHub repository.
+<!--Another Python-based simulation will soon be made available on Binder, but the preliminary code is already in the GitHub repository.-->
 
@@
 
-1. **manipulation effect size:** the effect size from the manipulation of interest
-2. **confound feature size:** the measured size of the confounding feature
-3. **confound feature-effect correlation:**the correlation between that measured size the and the effect size of the feature
+1. **manipulation effect size:** the effect size from the manipulation of interest (given as Cohen's $d$ between groups)
+2. **confound size:** the measured size of the confounding feature (given as Cohen's $d$ between groups)
+3. **confound-outcome correlation:** the simple correlation between that the confound size and the outcome (given as Pearson's $r$)
 
@@
 In other words, you're assuming that the measured feature difference exactly correlates with the impact that feature has on the outcome, which is a fairly strong assumption.
+
+In other words, the confound-outcome correlation is the actual effect size of the confounding variable, taken together with the confound size, you can compute the actual impact of confounding on the manipulation.
 
@@
 Both the source code and an explanation of the general principles (`simulation_notes.md`) are available in the GitHub repository.
-Here, we only need to iterate over a few possibilities for the manipulation effect size, confound feature size and confound feature-effect correlation.
+Here, we only need to iterate over a few possibilities for the manipulation effect size, confound size, and confound-outcome  correlation.
 The number of simulated experiments is held constant for all combinations of these (set via the document parameter `n`, which had the value `r params$n` when this document was generated).
@@
 ## Generate graphics
-```{r generate.graphics, dependson='simulate',cache=TRUE,message=FALSE}
+```{r generate.graphics, dependson='simulate',cache=TRUE,message=FALSE,warning=FALSE}
 # prettier names for the legend
@@
   }else if (variable == 'cfec') {
-    lbl <- paste("Feature-size/effect correlation:",value)
+    lbl <- paste("Feature-outcome correlation",value)
   } else {
@@
   facet_grid(cfs ~ mes,labeller = facet_labeller) + 
-  xlab("Correlation of feature as measured and effect of feature on outcome") + 
+  xlab("Correlation of confounding feature and dependent variable") + 
   ylab("Percent of simulated studies") + 
-  theme(legend.position="top") + #coord_fixed(ratio=1/100) +
-  guides(color=guide_legend(title="Result based on inferential pretesting of measured feature",
+  theme(legend.position="top", axis.text.x = element_text(angle = 45, hjust = 1), strip.text.y = element_text(angle=0)) + #coord_fixed(ratio=1/100) +
+  guides(color=guide_legend(title="Result based on inferential pretesting of confounding feature",
                             title.position="top",
@@
 ## Acceptances
-* Acceptances where the feature still had an effect in multiple rejection are failed detections of a real confounding effect.
-* Acceptances where the manipulation was only significant in simple regression are failed detections of a real confounding effect *that completes subsumes the manipulation effect*.
+* Acceptances where the feature still had an effect in multiple rejection are failed detections of a real confound.
+* Acceptances where the manipulation was only significant in simple regression are failed detections of a real confound *that completely subsumes the manipulation effect*.
 

### 2016-07-06 simulation/statfail.Rmd
republish on RPubs

@@
 ---
-title: 'A common misapplication of statistical inference: nuisance control with null-hypothesis significance test'
+title: 'A common misapplication of statistical inference: nuisance control with null-hypothesis significance tests'
 author: "Phillip M. Alday"
-date: "May  2016"
+date: "July  2016"
 output: 

### 2016-07-25 simulation/server.R
show "Accepted studies" in repated simulation results

@@ -303,11 +303,12 @@ shinyServer(function(input, output, session) {
     feature_has_no_effect <- sum(with(subset(cmp,pretest), !feature.simple))
     feature_irrelevant_in_multiple <- sum(with(subset(cmp,pretest), !feature.multiple))
 
-    vals <- c(rejections, manipulation_still_significant, feature_has_no_effect, feature_irrelevant_in_multiple)
+    vals <- c(n-rejections, rejections, manipulation_still_significant, feature_has_no_effect, feature_irrelevant_in_multiple)
 
     out <- data.frame(count=vals,percentage=signif(vals/n,2)*100)
 
-    rownames(out) <- c("Rejected studies"
+    rownames(out) <- c("Accepted studies"
+                       ,"Rejected studies"
                        ,"where the manipulation was still significant in the multiple regression"
                        ,"where the feature had no effect on the outcome in simple regression"
                        ,"where the feature was irrelevant in the multiple regression")

### 2016-07-25 simulation/server.R
fix rounding issue

@@ -305,7 +305,7 @@ shinyServer(function(input, output, session) {
 
     vals <- c(n-rejections, rejections, manipulation_still_significant, feature_has_no_effect, feature_irrelevant_in_multiple)
 
-    out <- data.frame(count=vals,percentage=signif(vals/n,2)*100)
+    out <- data.frame(count=vals,percentage=round(vals/n,4)*100)
 
     rownames(out) <- c("Accepted studies"
                        ,"Rejected studies"

### 2016-07-25 simulation/ui.R
use html output of original markdown so that references are expanded

@@ -90,7 +90,7 @@ shinyUI(fluidPage(
                   # )
           )
           ,tabPanel("Simulation notes",includeMarkdown("simulation_notes.md"))
-          ,tabPanel("Theoretical background",includeMarkdown("inference_failure.md"))
+          ,tabPanel("Theoretical background",includeHTML("inference_failure.html"))
           ,tabPanel("About",includeMarkdown("about.md"))
        )
     )

### 2016-07-25 simulation/statfail.Rmd
better scope for "only"

@@
                                        ,"but feature still had an effect in multiple regression",
-                                       "and the manipulation was only significant in simple regression"))
+                                       "and the manipulation was significant only in simple regression"))
 

### 2016-07-25 simulation/server.R
full output of accepted studies in ShinyApp

@@ -303,15 +303,23 @@ shinyServer(function(input, output, session) {
     feature_has_no_effect <- sum(with(subset(cmp,pretest), !feature.simple))
     feature_irrelevant_in_multiple <- sum(with(subset(cmp,pretest), !feature.multiple))
 
-    vals <- c(n-rejections, rejections, manipulation_still_significant, feature_has_no_effect, feature_irrelevant_in_multiple)
+    not_rejected <-  sum(!cmp$pretest)
+    feature_relevant_in_multiple <- sum(with(subset(cmp,!pretest), feature.multiple))
+    manipulation_only_in_simple <-  sum(with(subset(cmp,!pretest), manipulation.simple & !manipulation.multiple))
+
+    vals <- c(rejections, manipulation_still_significant, feature_has_no_effect, feature_irrelevant_in_multiple
+              ,not_rejected,feature_relevant_in_multiple,manipulation_only_in_simple)
 
     out <- data.frame(count=vals,percentage=round(vals/n,4)*100)
 
-    rownames(out) <- c("Accepted studies"
-                       ,"Rejected studies"
-                       ,"where the manipulation was still significant in the multiple regression"
+    rownames(out) <- c("Rejected studies"
+                       ,"where the manipulation was still significant in multiple regression"
                        ,"where the feature had no effect on the outcome in simple regression"
-                       ,"where the feature was irrelevant in the multiple regression")
+                       ,"where the feature was irrelevant in multiple regression"
+                       ,"Accepted studies"
+                       ,"where the feature still had an effect in multiple regression"
+                       ,"where the manipulation was significant only in simple regression"
+                       )
 
     out
   })

### 2016-08-02 poster-snl2016.tex
initial poster draft

% !TEX encoding = UTF-8
% !TEX spellcheck = en_US
\documentclass[final]{beamer}
\usepackage[utf8x]{inputenc}
\usepackage{lmodern}
\usepackage{exscale} % fixes some issues with lmodern in math mode
\usepackage[T1]{fontenc}
\usetheme{RJHlandscape}
\usepackage[orientation=landscape,size=a0,scale=1.4]{beamerposter}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,decorations.markings,positioning}
\tikzset{>=stealth}

\usepackage[absolute,overlay]{textpos}
\usepackage[numbers,compress]{natbib}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
%\usepackage{wrapfig}
\usepackage{rotating}

\graphicspath{{figures/}}

\newcolumntype{C}[1]{>{\centering\arraybackslash} m{#1} }
\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}
\newcommand{\subblock}[1]{\bigskip\textbf{#1}}

\title{Confound and control in language experiments}
\author{Phillip M. Alday  \and Jona Sassenhagen}
\institute{University of South Australia}
\footer{}
%\footer{Live code at \url{https://github.com/jona-sassenhagen/phijona---gamma}}
\date{}

\newcommand{\tikzmark}[3][]{\tikz[overlay,remember picture,baseline] \node [anchor=base,#1](#2) {#3};}
%\DeclareMathOperator*{\Pr}{Pr}
% color blind safe colours, see http://www.cookbook-r.com/Graphs/Colors_%28ggplot2%29/#a-colorblind-friendly-palette
\definecolor{lightorange}{HTML}{E69F00}
\definecolor{lightblue}{HTML}{56B4E9}
\definecolor{lightgreen}{HTML}{009E73}
\definecolor{lightyellow}{HTML}{F0E442}
\definecolor{darkblue}{HTML}{0072B2}
\definecolor{darkorange}{HTML}{D55E00}
\definecolor{darkpink}{HTML}{CC79A7}

\begin{document}
\begin{frame}{}

\begin{textblock}{48}(1,7)

\begin{block}{Introduction}
%Experimental research on the neurobiology of language depends on stimulus or participant selection where not all characteristics can be fully controlled, even when attempting strict matching.
Inferential statistics are often used to demonstrate that  confounding covariates do not differ systematically between groups:

\begin{quote}
Animate and inanimate words chosen as stimulus materials did not differ in word frequency (p > 0.05).

Controls and aphasics did not differ in age (p > 0.05).
\end{quote}

%In linguistic stimuli, factors such as word frequency are often correlated with primary factors of interest, such as animacy, or other co-confounds such as word length.
%In clinical studies, factors such as intelligence or socioeconomic status are often correlated with pathology.

%For example, if word length is not significantly different for two conditions, they are considered as matched for word length.
Such a test has high error rates and is conceptually misguided yet is commonly used (67\% of papers in a survey of recent Brain and Language issues).
\end{block}

\begin{block}{The stages of failure}
\begin{description}
\item[Philosophy] You can’t accept the null in NHST, only fail to reject it.
\item[Statistics] You’re violating testing assumptions because by design you did not randomly sample and even if had, you're performing inferences on a population you don’t care about.
\item[Pragmatics] You’re failing to perform the inference you actually care about (the impact of the confounding covariate on the dependent measure).
\end{description}
\end{block}

\begin{block}{Do you see what you've been missing?}
\begin{center}
\begin{tabular}{l l l }
\centering
What you're testing & What you worry about & What you care about \\
\includegraphics[width=0.3\textwidth]{feature.pdf}  & \includegraphics[width=0.3\textwidth]{feature_regression.pdf} & \includegraphics[width=0.3\textwidth]{anova.pdf} \\
\end{tabular}

What you should be doing:\\
 \includegraphics[width=1\textwidth]{multiple_regression.pdf} 
\end{center}

\tiny
\hfill Effect size: Cohen's $d=2$, confound size Cohen's  $d=1$, confound-outcome correlation: Pearson's $r=1$

\end{block}

\begin{block}{Interesting Interactions}
Complex interactions make completely unconfounded studies difficult. 
For example, marked constructions are generally less frequent than unmarked ones, leading to the claim that observed differences in processing are frequency effects.
Modelling our confounds directly allows us to examine the piecewise contributions from the experimental manipulation and the 'confound'.
\end{block}

\end{textblock}

\begin{textblock}{48}(50.5,7)

\begin{block}{Wasted stimuli}
\includegraphics{rejections.png}
\end{block}

\begin{block}{Missed confounds}
\includegraphics{acceptances.png}
\end{block}

\end{textblock}

\begin{textblock}{18}(100,7)

\begin{block}{Getting things under control}
Match descriptive statistics (measures of central location such as mean and median, as well as variance).

\vspace{0.8cm}

Include a 'nuisance' covariate in an appropriate statistical model, such as a mixed-effects model.

\vspace{0.8cm}

The actual impact of the confound can be examined both by its associated model parameters and by comparison between models with and without the nuisance covariate.

\vspace{0.8cm}

\textbf{Appropriate model selection is the way to determine the influence of confounds.}

\end{block}

%\begin{block}{Literature}
%\tiny
%\bibliographystyle{poster}
%\bibliography{snl2016.bib}
%\vspace{0.25cm}
%\end{block}

\begin{block}{Try the app!}
\centering
\includegraphics[width=0.6\textwidth]{shinyapps-url.eps}
%
%http://rpubs.com/palday/statfail
\end{block}

\begin{block}{Read the preprint!}
\centering
\includegraphics[width=0.6\textwidth]{arxiv-url.eps}
%

\end{block}

\begin{block}{}
\begin{tabular}{c c c}
\includegraphics[width=.55\linewidth]{logo_unisa_RGB-blue.png} &   \includegraphics[width=.4\linewidth]{cnl-color.eps} & \\
\end{tabular}

%\includegraphics[width=.9\linewidth]{logo_mainz_new.eps}
\end{block}

\end{textblock}

\end{frame}
\end{document}

### 2016-08-02 generateQRsnl2016.py

@@ -1,0 +1,6 @@
+import pyqrcode
+import os.path
+url = pyqrcode.create('https://arxiv.org/abs/1602.04565')
+url.eps(os.path.join('figures','arxiv-url.eps'), scale=2) 
+url = pyqrcode.create('https://palday.shinyapps.io/statfail/')
+url.eps(os.path.join('figures','shinyapps-url.eps'), scale=2) 

### 2016-08-02 snl2016.R

@@ -1,0 +1,58 @@
+library(ggplot2)
+library(car)
+library(plyr)
+library(reshape2)
+
+source("simulation/statfail.R")
+set.seed(42)
+
+results <- resimulate(n=1
+                      ,manipulation.effect.size=2
+                      ,confound.feature.size=1
+                      ,confound.feature.effect.correlation=1
+                      ,n.items=20)
+results$condition <- factor(results$condition,levels=c("control","manipulation"))
+# since there are no other categorical variables to interact with, we keep
+# it simple and use treatment coding. This allows a few shortcuts later, where
+# we assume that the control=0 and treatment=1
+options(decorate.contr.Treatment = "")
+contrasts(results$condition) <- contr.Treatment(levels(results$condition))
+
+g <- ggplot(results,aes(color=condition,fill=condition,x=feature)) +
+  geom_density(alpha=0.4) +
+  #geom_histogram(alpha=0.4) +
+  geom_rug(size=1.5,alpha=0.4) +
+  #scale_color_discrete(name="Condition",labels=c("control","manipulation")) +
+  guides(fill="none",color="none") +
+  ggtitle("Feature distribution") + theme(legend.position = "none")
+
+ggsave("figures/feature.pdf",g,height=4,width=4)
+
+g <- ggplot(results,aes(x=as.numeric(condition)-1,y=confounded.outcome)) +
+  geom_smooth(method=lm) +
+  geom_point(aes(color=condition),alpha=0.4) +
+  scale_x_continuous("condition",breaks=c(0,1),labels=c("control","manipulation")) +
+  ylab("outcome") +
+  ggtitle("ANOVA for manipulation") + theme(legend.position = "none")
+
+ggsave("figures/anova.pdf",g,height=4,width=4)
+
+g <- ggplot(results,aes(x=feature,y=confounded.outcome)) +
+  geom_smooth(method=lm) +
+  geom_point(aes(color=condition),alpha=0.4) +
+  ylab("outcome") +
+  ggtitle("Regression for feature") + theme(legend.position = "none")
+
+ggsave("figures/feature_regression.pdf",g,height=4,width=4)
+
+g <- ggplot(results,aes(x=feature,y=confounded.outcome,color=condition,fill=condition)) +
+  geom_smooth(method=lm,fullrange=TRUE) +
+  geom_point(alpha=0.4) +
+  ylab("outcome") +
+  guides(fill="none",color="none") +
[…]

### 2016-08-02 poster-snl2016.tex
frankfurt logos

@@
 \centering
-\includegraphics[width=0.6\textwidth]{shinyapps-url.eps}
+\includegraphics[width=0.55\textwidth]{shinyapps-url.eps}
 %
@@
 \centering
-\includegraphics[width=0.6\textwidth]{arxiv-url.eps}
+\includegraphics[width=0.55\textwidth]{arxiv-url.eps}
 %
@@
 \begin{block}{}
-\begin{tabular}{c c c}
-\includegraphics[width=.55\linewidth]{logo_unisa_RGB-blue.png} &   \includegraphics[width=.4\linewidth]{cnl-color.eps} & \\
+\begin{tabular}{c c }
+\includegraphics[width=.55\linewidth]{logo_unisa_RGB-blue.png} &   \includegraphics[width=.3\linewidth]{cnl-color.eps}  \\
+\includegraphics[width=.4\linewidth]{logo_frankfurt_square.png} & \includegraphics[width=.4\linewidth]{logo_fiebach_lab.png} \\
 \end{tabular}

### 2016-08-02 poster-snl2016.tex
small technicality on percentage

@@
 %For example, if word length is not significantly different for two conditions, they are considered as matched for word length.
-Such a test has high error rates and is conceptually misguided yet is commonly used (67\% of papers in a survey of recent Brain and Language issues).
+Such a test has high error rates and is conceptually misguided yet is commonly used (67\% of papers attempting to address confounding in a survey of recent Brain and Language issues).
 \end{block}

### 2016-08-05 poster-snl2016.tex
bottom edge spacing
latex quotes

@@
 For example, marked constructions are generally less frequent than unmarked ones, leading to the claim that observed differences in processing are frequency effects.
-Modelling our confounds directly allows us to examine the piecewise contributions from the experimental manipulation and the 'confound'.
+Modelling our confounds directly allows us to examine the piecewise contributions from the experimental manipulation and the `confound'.
+
+\vspace{.38cm}
 \end{block}
@@
 
-Include a 'nuisance' covariate in an appropriate statistical model, such as a mixed-effects model.
+Include a `nuisance' covariate in an appropriate statistical model, such as a mixed-effects model.
 
@@
 
+\vspace{0.4cm}
+
 %\includegraphics[width=.9\linewidth]{logo_mainz_new.eps}
